\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-09-17 manuscript/cov.tex
cover letter for General section of TAS

\documentclass{article}
\usepackage{charter}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr,graphicx}
\usepackage{xspace}

@@

\hfill
\begin{tabular}{ l @{} }
  \today \\[12pt] % Date
  Department of Statistics,\\
  University of Connecticut\\
  Room 323, Philip E. Austin Building\\
  215 Glenbrook Road, Unit 4120\\
  Storrs, CT 06269-4120\\
  \\
  Department of Statistics and Data Science,\\
  University of California, Los Angeles\\
  8125 Math Sciences Bldg. Box 951554\\
  Los Angeles, CA 90095-1554\\
  \\
  Department of Statistics,\\
  Texas A\&M University\\
  447 Blocker Building (BLOC)\\
  3143 TAMU | 155 Ireland St\\
  College Station, TX 77843-3143
\end{tabular}

@@

We are pleased to submit the manuscript entitled ``Nonparametric Block Bootstrap 
Kolmogorov-Smirnov Goodness-of-Fit Test" for 
consideration in the Statistical Practice section of 
\textit{American Statistician}. We certify that this 
manuscript has neither been published nor is under consideration by another 
journal.

Our paper introduces a novel approach
which can widen the applications of the Kolmogorov--Smirnov (KS) test, a 
goodness-of-fit test which relies on the data
being serially dependent and the parameters for the hypothesized distribution
being specified.

This paper introduces a bias correction for the test based on the non-parametric 
block bootstrap that accounts for serial dependence and does not require
specification of parameters.
The main contribution is a new methodological development which is useful
for addressing a broad array of
practical problems in financial analysis, environmental science, as 
well as other situations that require goodness-of-fit tests on serially
dependent data. An application of our method to test the distribution
of S\&P 500 index stock returns is shown in the manuscript.

This article will prove to be a valuable expansion to statistical practice.
Please feel free to reach out to us if you need any other information concerning 
this manuscript.

@@

\vspace{50pt}

>>>>

\documentclass[12pt]{article}
\usepackage{charter}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr,graphicx}
\usepackage{xspace}

@@

\hfill
\begin{tabular}{ l @{} }
  \today \\[12pt] % Date
  Department of Statistics and Data Science,\\
  University of California, Los Angeles\\
  8125 Math Sciences Bldg. Box 951554\\
  Los Angeles, CA 90095-1554
\end{tabular}

@@

We are pleased to submit our manuscript entitled 
``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit
Test"  for consideration in the \emph{General} Section of the
\textit{American Statistician}. We certify that this manuscript has
neither been published nor is under consideration by any other
journal.

Our paper addresses a gap in the application of the Kolmogorov-Smirnov
(KS) test for assessing the marginal goodness-of-fit of hypothesized
distributions in the context of serially dependent stationary
observations. While parametric block bootstrap procedures typically
require specification of the serial dependence structure, a
nonparametric block bootstrap procedure is advantageous as it avoids
this requirement. The nonparametric block bootstrap version of the KS
test extends the nonparametric approach studied by Basu and Rao
(2004) to cases of serial dependence. However, such a version does not
yet exist, and our paper fills this gap. The proposed test has wide
applications in time series modeling, particularly in scenarios where
marginal distributions are of interest, such as in financial time series.

We believe that the methodological developments in this manuscript are
of broad interest and are generally not highly technical, making it a
suitable fit for the \emph{General} Section of your journal.

Thank you for your consideration, and we look forward to your feedback.

@@

\vspace{2cm}
